Run-Time Monitoring with Adjustable Overheads \\Using Dataflow-Guided Filtering

### 2014-09-13 conclusion.tex
Minor edits.

Parallel run-time monitoring techniques are attractive solutions for improving
the reliability, security, and debugging capabilities of systems. In this
paper, we have presented an architecture that enables adjustable overheads through partial monitoring. 
The architecture uses a dataflow tracking engine to prevent false positives
through tracking invalidation information. In addition, we show how the
architecture can be extended to enable null metadata filtering.
Given this architecture, we explore the design choices related to the dropping policy.
With partial monitoring, we see that with a 1.5x overhead target, BC can still
achieve 82\% average coverage and UMC can still achieve 43\% average coverage.
At this overhead target, IMP shows less than 3\% error on average.
With a 1.2x overhead target, LS achieves over 70\% average coverage.

>>>>

Parallel run-time monitoring techniques are attractive solutions for improving
the reliability, security, and debugging capabilities of systems. In this
paper, we have presented an architecture that enables adjustable overheads through partial monitoring. 
The architecture uses a dataflow tracking engine to prevent false positives
through tracking invalidation information. In addition, we show how the
architecture can be extended to enable null metadata filtering.
Given this architecture, we explore the design choices related to the dropping policy.
With partial monitoring, we see that with a 1.5x overhead target, BC can still
achieve 82\% average coverage and UMC and LS can still achieve 43\%  and 94\%
average coverage respectively.
At this overhead target, IMP shows less than 3\% error on average.

### 2014-09-13 dropping.tex
Minor edits.

Figure~\ref{fig:dropping.example_full} shows an example pseudo-code segment,
its assembly level instructions, and the corresponding monitoring operations
for an array bounds check monitor. 
First, an array {\tt x} is allocated using {\tt malloc} (line 1). 
As {\tt malloc} returns the array's address in a register, the monitor
associates base and bounds metadata with the corresponding register. 
Next, pointer {\tt y} is set to point to the middle of array {\tt x} (line 2). 
At the assembly level, a register {\tt r2} is set to array {\tt x}'s address plus an offset.
The monitor propagates the metadata of the original pointer in {\tt r1} to the
metadata of {\tt r2}. This is to ensure that pointer {\tt y} is not used to exceed the array's bounds.
Line 3a shows setting register {\tt r3} to a constant value of 1.
When this happens,
{\tt r3}'s metadata is also reset to NULL in case it previously stored a
pointer. 
Finally, the value of {\tt r3} is written to memory using both pointers {\tt x} and {\tt y}.
In both cases, the monitor checks whether the store address is within the bounds of the register metadata. In the first case (line 3b), {\tt x+12}
is within the original array's bounds. No error is raised and the metadata of
{\tt r3} is propagated to the metadata of the store address. If {\tt r3} were a
pointer, then this would allow a future instruction to load the pointer and use
it to access the corresponding array or data structure. In the second case,
{\tt y+12} (line 4) corresponds to {\tt x+20} which is not within the array's bounds and
the monitor will raise an error.

@@

The key cause of false positives is dropping monitoring operations that update
metadata. Dropping monitoring operations that check for an error (such as the check
for line 4 in Figure~\ref{fig:dropping.example_full}) can only cause
false negatives but will never cause false positives. On the other hand,
skipping monitoring operations that update metadata can lead to false positives
and false negatives.
Essentially, when an update operation is skipped, we can no longer trust the
corresponding metadata. Thus, our general approach for preventing false
positives is to associate a 1-bit flag with each metadata in order to mark these
metadata as valid or
invalid. Furthermore, this invalidation information is propagated in the same
way that metadata is. Figure~\ref{fig:dropping.example_invalid}
shows an example of associating invalid flags with metadata. In the example, no
monitoring operations are dropped. However, suppose that the monitoring for
line 1 is dropped. When a monitoring event is dropped, metadata that would have
been updated is marked as invalid. In this case, {\tt rf\_invalid[1]} will be
marked as {\tt
true}. Thus, when line 3 is reached, the monitoring event is dropped
since {\tt rf\_invalid[1]} is marked as true. Note that in this case, line 2
also propagates this invalid flag to {\tt rf\_invalid[2]} and causes the check
performed on line 4 to also be dropped. This is necessary because an error
would have been raised even if the access on line 4 was in bounds.

@@

Figure~\ref{fig:dropping.example_null} shows an example of how this null filtering operates.
Here, the main core's code has been slightly modified from
Figure~\ref{fig:dropping.example_full} and {\tt r2} on line 2 is no longer set as an array pointer.
Without null metadata filtering, the instructions for lines 2 and 4 would be
forwarded to the monitor since the system does not know whether {\tt r2}
contains a pointer address or not. However, if we use a 1-bit flag to mark {\tt r2}
as null when it is loaded with a constant, then we can propagate this null
information and filter out monitoring for lines 2 and 4.

>>>>

Figure~\ref{fig:dropping.example_full} shows an example pseudo-code segment,
its assembly level instructions, and the corresponding monitoring operations
for an array bounds check monitor. 
First, an array {\tt x} is allocated using {\tt malloc} (line 1). 
As {\tt malloc} returns the array's address in a register, the monitor
associates base and bounds metadata with the corresponding register. 
Next, pointer {\tt y} is set to point to the middle of array {\tt x} (line 2). 
At the assembly level, a register {\tt r2} is set to array {\tt x}'s address plus an offset.
The monitor propagates the metadata of the original pointer in {\tt r1} to the
metadata of {\tt r2}. This is to ensure that pointer {\tt y} is not used to exceed the array's bounds.
Line 3a shows setting register {\tt r3} to a constant value of 1.
When this happens,
{\tt r3}'s metadata is reset to NULL in case it previously stored a
pointer. 
Finally, the value of {\tt r3} is written to memory using both pointers {\tt x} and {\tt y}.
In both cases, the monitor checks whether the store address is within the bounds of the register metadata. In the first case (line 3b), {\tt x+12}
is within the original array's bounds. No error is raised and the metadata of
{\tt r3} is propagated to the metadata of the store address. If {\tt r3} were a
pointer, then this would allow a future instruction to load the pointer and use
it to access the corresponding array or data structure. In the second case,
{\tt y+12} (line 4) corresponds to {\tt x+20} which is not within the array's bounds and
the monitor will raise an error.

@@

The key cause of false positives is dropping monitoring operations that update
metadata. Dropping monitoring operations that check for an error (such as the check
for line 4 in Figure~\ref{fig:dropping.example_full}) can only cause
false negatives but will never cause false positives. On the other hand,
skipping monitoring operations that update metadata can lead to false positives
and false negatives.
Essentially, when an update operation is skipped, we can no longer trust the
corresponding metadata. Thus, our general approach for preventing false
positives is to associate a 1-bit flag with each metadata in order to mark these
metadata as valid or
invalid. Furthermore, this invalidation information is propagated in the same
way that metadata is. Figure~\ref{fig:dropping.example_invalid}
shows an example of associating invalid flags with metadata. Suppose that the monitoring for
line 1 is dropped. When a monitoring event is dropped, metadata that would have
been updated is marked as invalid. In this case, instead of the normal
operation of marking {\tt rf\_invalid[1]} as {\tt false}, it is instead
marked as {\tt
true}. Thus, when line 3 is reached, the monitoring event is dropped
since {\tt rf\_invalid[1]} is marked as true. Note that in this case, line 2
also propagates this invalid flag to {\tt rf\_invalid[2]} and causes the check
performed on line 4 to also be dropped. This is necessary because an error
would have been raised even if the access on line 4 was in bounds.

@@

Figure~\ref{fig:dropping.example_null} shows an example of how this null filtering operates.
Here, the main core's code has been slightly modified from
Figure~\ref{fig:dropping.example_full} and {\tt r2} on line 2 is no longer set as an array pointer.
Without null metadata filtering, the instruction for line 4 would be
forwarded to the monitor since the system does not know whether {\tt r2}
contains a pointer address or not. However, if we use a 1-bit flag to mark {\tt r2}
as null when it is loaded with a constant, then we can propagate this null
information and filter out monitoring for line 4.

### 2014-09-13 evaluation.tex
Minor edits.

Since LockSet race detection requires multi-threaded programs, we tested it using
the applications from the SPLASH-2 benchmark set \cite{splash-isca95}. We ran these benchmarks for
200 million instructions with 2 main cores running the benchmark application.
Each main core was connected to a dataflow engine and a monitoring core.

@@

Figure~\ref{fig:evaluation.filtering} shows the
execution times of performing monitoring with null filtering enabled normalized
to the execution time of the benchmarks without monitoring. UMC sees normalized
execution times of 1.7-7x with an average of 4x.
For BC, normalized execution
are 3x on average and range from 1.1x to 8.3x.
% This is not surprising since in the baseline
% implementation all loads and stores needed to be monitored. However, with
% filtering, only loads and stores corresponding to arrays need to be forwarded.
DIFT sees an average of 1.1x slowdown with a maximum slowdown of 1.3x with null
metadata filtering. This low overhead is due, in part, to the fact
that for our implementation of DIFT on SPEC
benchmarks, we only mark data read from files as tainted. Instead, if we
targeted network or streaming applications, which have larger amounts of
untrusted input data, we would higher overheads. IMP shows normalized
execution times of 2-6x with an average of 4x. Overheads for LS (not pictured) are
1.03-1.72x after null metadata filtering and the average
overhead observed is 1.33x for the SPLASH-2 benchmarks.
Our baseline system and overheads are similar to previous multi-core
monitoring systems such as LBA-accelerated \cite{lba-isca08} and FADE
\cite{fade-hpca14} (see
Table~\ref{tab:monitoring.previous_overheads}). In
Section~\ref{sec:evaluation.fpga}, we also evaluate a higher performance, FPGA-based
monitor that shows low tens of percent of overhead.

@@

In this section, we evaluate the effectiveness of
using partial monitoring to trade-off coverage for reduced overheads.
For these results, we use a slack-based, unrestricted dropping policy.
Figure~\ref{fig:evaluation.bc_sweep} shows the monitoring coverage achieved by
array bounds check as we vary the overhead budget. The bottom portion of each
bar shows the coverage for a 1.1x overhead target and the additional
coverage for increased overhead targets are stacked above this.
We define \emph{monitoring coverage} as the 
percentage of dynamic checks that are performed 
(indirect jumps in DIFT, loads in UMC, and memory accesses in BC and LS). 
The metric is chosen to understand
how likely an error/attack instance is to be detected on an individual system, 
assuming that errors/attacks are uniformly distributed across checks. 
%While we could not evaluate real errors/attacks due to difficulty in setting up
%a large number of bugs and exploits, we believe that the percentage of checks
%provides a good estimate of detection probability when errors/attacks are 
%uniformly distributed across checks.
Note that this metric is different from the
percentage of monitoring events that are not dropped, which includes
non-check instructions.

@@

The instruction-mix profiling monitor does not perform check operations. Thus,
the concept of coverage is not applicable here. Instead, for each instruction
type profiled, we calculate its count as a percentage of the total instructions
monitored. We take the difference of these percentages compared to the case
when full monitoring
is performed to calculate the error. Figure~\ref{fig:evaluation.imp_sweep}
shows the min, max, and average error across
instruction types for each benchmark and for varying overheads. We see that
with a 1.1x overhead a max error of 9\% is observed across benchmarks and the
average error across instruction types and benchmarks is less than 2\%.

@@

Next, we evaluate these trade-offs between source-only dropping and unrestricted dropping for BC.
Figure~\ref{fig:evaluation.bc_exec_time} shows the overhead differences for BC
and Figure~\ref{fig:evaluation.bc_coverage} shows the coverage for BC.
From Figure~\ref{fig:evaluation.bc_exec_time}, we see that for several
benchmarks, source-only drop fails to meet the specified overhead target.
The overshoot of the overhead target is quite high with an overhead differences
of 420\% for {\tt bzip2}, 120\% for {\tt gcc}, and 1500\% for {\tt hmmer}.
Since only array allocations, which are infrequent, are considered as source events for BC, it is
difficult for source-only dropping to match overhead targets. Although
Figure~\ref{fig:evaluation.bc_coverage} shows higher coverage for
source-only dropping, this is largely due to the fact that is running with
higher overheads.

From these results, we see that for monitors with many short, independent
chains, such as UMC, source-only dropping can provide better coverage than
unrestricted dropping with the same overhead. For other monitors, such as BC,
source-only dropping is prone to overshoot the overhead target.
Thus, for applications where staying with an overhead target is especially
important, such as soft real-time systems, a slack-based, unrestricted dropping
policy is more appropriate. On the other hand, if maximum coverage is desired
and occasional slowdowns are acceptable, then source-only dropping can provide
better coverage on average.

@@

One application of partial monitoring with low overheads is to enable
cooperative debugging. 
The idea with cooperative debugging is to use partial
monitoring with very low overheads across a large number of users or runs. By
varying the pattern of partial monitoring done on each run, the goal is to
achieve high coverage across multiple runs. Varying the monitoring that is
done for different runs can be achieved by using a probabilistic dropping policy.
Figure~\ref{fig:evaluation.multirun} shows the total
coverage achieved over multiple runs for array bounds check running for
unrestricted and source-only dropping policies with probabilistic dropping.
These numbers are averaged across all benchmarks. Here, we use a 10\%
probability
that events are not dropped. Since the goal is code coverage, coverage here is
measured as the percentage of static instructions which are monitored in at
least one of the runs. Each run
was simulated for 200 million instructions. 
We see that for the unrestricted dropping policy there is almost no increase in
coverage.  This is due to the fact that it is likely that at least one
monitoring event in a metadata dependence chain will be dropped with the unrestricted dropping
policy. 
Instead, source-only
dropping is much better suited for achieving high coverage over multiple runs.
Source-only dropping shows a 5\% increase in coverage with only seven runs.
Over many runs, source-only dropping should be able to
reach 100\% code coverage.

>>>>

Since LockSet race detection requires multi-threaded programs, we tested it using
the applications from the SPLASH-2 benchmark set \cite{splash-isca95}. We ran these benchmarks for
200 million instructions eachi using 2 main cores to run the benchmark application.
Each main core was connected to a dataflow engine and a monitoring core.

@@

Figure~\ref{fig:evaluation.filtering} shows the
execution times of performing monitoring with null filtering enabled normalized
to the execution time of the benchmarks without monitoring. UMC sees normalized
execution times of 1.7-7x with an average of 4x.
For BC, normalized execution
are 3x on average and range from 1.1x to 8.3x.
% This is not surprising since in the baseline
% implementation all loads and stores needed to be monitored. However, with
% filtering, only loads and stores corresponding to arrays need to be forwarded.
DIFT sees an average of 1.1x slowdown with a maximum slowdown of 1.3x with null
metadata filtering. This low overhead is due, in part, to the fact
that for our implementation of DIFT on SPEC
benchmarks, we only mark data read from files as tainted. Instead, if we
targeted network or streaming applications, which have larger amounts of
untrusted input data, we would observe higher overheads. IMP shows normalized
execution times of 2-6x with an average of 4x. Overheads for LS (not pictured)
applied to the SPLASH-2 benchmarks are
1.03-1.72x after null metadata filtering and the average
overhead observed is 1.33x.
Our baseline system and overheads are similar to previous multi-core
monitoring systems such as LBA-accelerated \cite{lba-isca08} and FADE
\cite{fade-hpca14} (see
Table~\ref{tab:monitoring.previous_overheads}). In
Section~\ref{sec:evaluation.fpga}, we also evaluate a higher performance, FPGA-based
monitor that shows low tens of percent of overhead.

@@

In this section, we evaluate the effectiveness of
using partial monitoring to trade-off coverage for reduced overheads.
For these results, we use a slack-based, unrestricted dropping policy.
Figure~\ref{fig:evaluation.bc_sweep} shows the monitoring coverage achieved by
array bounds check as we vary the overhead budget. 
We define \emph{monitoring coverage} as the 
percentage of dynamic checks that are performed 
(indirect jumps in DIFT, loads in UMC, and memory accesses in BC and LS). 
The metric is chosen to understand
how likely an error/attack instance is to be detected on an individual system, 
assuming that errors/attacks are uniformly distributed across checks. 
%While we could not evaluate real errors/attacks due to difficulty in setting up
%a large number of bugs and exploits, we believe that the percentage of checks
%provides a good estimate of detection probability when errors/attacks are 
%uniformly distributed across checks.
Note that this metric is different from the
percentage of monitoring events that are not dropped, which includes
non-check instructions.
The bottom portion of each
bar shows the coverage for a 1.1x overhead target and the additional
coverage for increased overhead targets are stacked above this.

@@

The instruction-mix profiling monitor does not perform check operations. Thus,
the concept of coverage is not applicable here. Instead, for each instruction
type profiled, we calculate its count as a percentage of the total instructions
monitored. We take the difference of these percentages compared to the case
when full monitoring
is performed to calculate the error. Figure~\ref{fig:evaluation.imp_sweep}
shows the min, max, and average error across
instruction types for each benchmark and for varying overheads. We see that
with a 1.1x overhead, a max error of 9\% is observed across the benchmarks and the
average error across instruction types and benchmarks is less than 2\%.

@@

Next, we evaluate these trade-offs between source-only dropping and unrestricted dropping for BC.
Figure~\ref{fig:evaluation.bc_exec_time} shows the overhead differences for BC
and Figure~\ref{fig:evaluation.bc_coverage} shows the coverage for BC.
From Figure~\ref{fig:evaluation.bc_exec_time}, we see that for several
benchmarks, source-only dropping fails to meet the specified overhead target.
The overshoot of the overhead target is quite high with overhead differences
of 420\% for {\tt bzip2}, 120\% for {\tt gcc}, and 1500\% for {\tt hmmer}.
Since only infrequently occurring array allocations are considered as source events for BC, it can be 
difficult for source-only dropping to match overhead targets. Although
Figure~\ref{fig:evaluation.bc_coverage} shows higher coverage for
source-only dropping, this is largely due to the fact that is running with
higher overheads.

From these results, we see that for monitors with many short, independent
chains, such as UMC, source-only dropping can provide better coverage than
unrestricted dropping with the same overhead. For other monitors, such as BC,
source-only dropping is prone to overshoot the overhead target.
Thus, for applications where staying within an overhead target is especially
important, such as soft real-time systems, a slack-based, unrestricted dropping
policy is more appropriate. On the other hand, if maximum coverage is desired
and occasional slowdowns are acceptable, then source-only dropping can provide
better coverage on average.

@@

One application of partial monitoring with low overheads is to enable
cooperative debugging. 
The idea with cooperative debugging is to use partial
monitoring with very low overheads across a large number of users or runs. By
varying the pattern of partial monitoring done on each run, the goal is to
achieve high coverage across multiple runs. Varying the monitoring that is
done for different runs can be achieved by using a probabilistic dropping policy.
Figure~\ref{fig:evaluation.multirun} shows the total
coverage achieved over multiple runs for array bounds check using
unrestricted and source-only dropping policies with probabilistic dropping.
These numbers are averaged across all benchmarks. Here, we use a 10\%
probability
that events are not dropped. Since the goal is code coverage, coverage here is
measured as the percentage of static instructions which are monitored in at
least one of the runs. Each run
was simulated for 200 million instructions. 
We see that for the unrestricted dropping policy there is almost no increase in
coverage.  This is due to the fact that it is likely that at least one
monitoring event in a metadata dependence chain will be dropped with the unrestricted dropping
policy. 
Instead, source-only
dropping is much better suited for achieving high coverage over multiple runs.
Source-only dropping shows a 5\% increase in coverage with only seven runs.
Over many runs, source-only dropping should be able to
reach 100\% code coverage.

### 2014-09-13 monitoring.tex
Edits from Tao's comments.
Minor edits.

There have been a number of proposals for run-time monitoring systems exploring various
design points. % in the trade-off space between efficiency and flexibility.
Table~\ref{tab:monitoring.previous_overheads} summarizes some the of representative designs
and their reported performance overhead. The previous studies clearly show that there
exist trade-offs between efficiency, flexibility, and hardware costs. 
For example, a run-time monitoring scheme can often be realized with fairly low
performance overhead (less than 20\%) if implemented with custom hardware that is
designed only for one monitor or a narrow set of monitors. However, the custom
hardware monitors cannot be modified or updated, and require dedicated silicon area. 
On the other hand, flexible systems that support a wide range of monitors lead 
to noticeable performance overhead, often too high for wide deployment in practice.
Software-only implementations \cite{nagarajan-interact08, lift-micro06,
purify-usenix92, taintcheck-ndsss05} or multi-core monitors with minimal
hardware changes \cite{lba-asid06} are reported to have severalfold slowdowns.
On-chip FPGA monitors \cite{flexcore-micro10} and cores with monitoring accelerators
\cite{lba-isca08, fade-hpca14} can reduce overhead significantly, but still show
slowdowns of several tens of percents in some cases.
In today's monitoring systems, the overhead is also unpredictable because they
depend heavily on the characteristics of applications and monitoring operations.
In summary, users currently need to either pay noticeable overhead or the cost of custom
hardware in order to use fine-grained run-time monitoring in deployed systems.

@@

{\bf Cooperative testing, debugging, and protection:}
Recently, studies \cite{liblit-pldi05, chilimbi-asplos04, greathouse-cgo11, testudo-micro08} have shown that software testing, debugging,
or attack detection may be done in a cooperative fashion across
a large number of systems. In this case, each system is only willing to pay very low
overhead (e.g., a few percent) and only performs a small subset of checks. 
High coverage is achieved by having different systems check different parts of a program.
The partial monitoring framework allows high-overhead monitoring to be used in a
cooperative fashion. 
The main metric that represents the effectiveness of monitoring in this case is
the coverage (the percentage of checks there were performed) over multiple runs.

@@

{\bf Profiling:} 
The run-time monitoring system can be used to implement various profiling tools
to collect statistics on program behaviors for performance optimizations as well
as security protection. For example, a recent study showed that an instruction
mix can be used to identify malware from normal programs \cite{demme-isca13, tang-raid14}. 
In such profiling tools, the partial monitoring framework can be used to obtain
statistical samples rather than complete counts of all program events, essentially trading off
accuracy for lower overhead.

>>>>

There have been a number of proposals for run-time monitoring systems exploring various
design points. % in the trade-off space between efficiency and flexibility.
Table~\ref{tab:monitoring.previous_overheads} summarizes some of the representative designs
and their reported performance overhead. The previous studies clearly show that there
exist trade-offs between efficiency, flexibility, and hardware costs. 
For example, a run-time monitoring scheme can often be realized with fairly low
performance overhead (less than 20\%) if implemented with custom hardware that is
designed only for one monitor or a narrow set of monitors. However, the custom
hardware monitors cannot be modified or updated, and require dedicated silicon area. 
On the other hand, flexible systems that support a wide range of monitors lead 
to noticeable performance overhead, often too high for wide deployment in practice.
Software-only implementations \cite{nagarajan-interact08, lift-micro06,
purify-usenix92, taintcheck-ndsss05} or multi-core monitors with minimal
hardware changes \cite{lba-asid06} are reported to have severalfold slowdowns.
On-chip FPGA monitors \cite{flexcore-micro10} and cores with monitoring accelerators
\cite{lba-isca08, fade-hpca14} can reduce overhead significantly, but still show
slowdowns of several tens of percents in some cases.
In today's monitoring systems, the overheads are also unpredictable because they
depend heavily on the characteristics of applications and monitoring operations.
In summary, users currently need to either pay noticeable overhead or the cost of custom
hardware in order to use fine-grained run-time monitoring in deployed systems.

@@

{\bf Cooperative testing, debugging, and protection:}
Recently, studies \cite{liblit-pldi05, chilimbi-asplos04, greathouse-cgo11, testudo-micro08} have shown that software testing, debugging,
or attack detection may be done in a cooperative fashion across
a large number of systems. In this case, each system is only willing to pay very low
overhead (e.g., a few percent) and only performs a small subset of checks. 
High coverage is achieved by having different systems check different parts of a program.
The partial monitoring framework allows high-overhead monitoring to be used in a
cooperative fashion. 
The main metric that represents the effectiveness of monitoring in this case is
the coverage (the percentage of checks that were performed) over multiple runs.

@@

{\bf Profiling:} 
The run-time monitoring system can be used to implement various profiling tools
to collect statistics on program behavior for performance optimizations as well
as security protection. For example, a recent study showed that an instruction
mix can be used to identify malware from normal programs \cite{demme-isca13, tang-raid14}. 
In such profiling tools, the partial monitoring framework can be used to obtain
statistical samples rather than complete counts of all program events, essentially trading off
accuracy for lower overhead.

### 2014-09-13 policies.tex
Cut to 11 pages.
Minor edits.

\begin{figure}
  \begin{center}
  \subfloat[unrestricted dropping]{
    \includegraphics[width=\columnwidth]{figs/all_drop.pdf}
    \label{fig:policies.all_drop}
  }
  \vspace{-0.1in}
  \\
  \subfloat[source-only dropping]{
    \includegraphics[width=\columnwidth]{figs/source_drop.pdf}
    \label{fig:policies.source_drop}
  }
  \vspace{-0.1in}
%   \\
%   \subfloat[sub-flow dropping]{
%     \includegraphics[width=\columnwidth]{figs/min_drop.pdf}
%     \label{fig:policies.min_drop}
%   }
  \end{center}
  \vspace{-0.1in}
  \caption{Comparison of dropping policies using metadata dependence graphs.
  Square nodes represent events where check are performed. Blue (dark) nodes
  indicate which nodes can be dropped.}
  \label{fig:policies.policies}
\end{figure}

In addition to deciding when dropping is required, trade-offs also exist in
deciding which events should be dropped.
The simplest policy is to drop any monitoring events when slack is less than or equal to zero.  However, this can result in
wasted work. For example, consider the metadata dependence graph shown in
Figure~\ref{fig:policies.all_drop}. Here, an edge from node {\tt A} to node
{\tt B} represents that if event {\tt A} is dropped, then due to its
invalidated metadata, it will cause event {\tt B} to be dropped. Square
nodes indicate events where monitoring checks are performed. In the
example, suppose that event {\tt E} is meant to perform a check operation but is dropped.
In this situation, the
monitoring operations that were done for events {\tt C} and {\tt D} were wasted
since their results were not used for any monitoring checks.
That is, by the time we decide to drop event {\tt E}, we have already 
updated metadata due to events {\tt C} and {\tt D} which is no longer needed.

>>>>

\begin{figure}
  \begin{center}
  \subfloat[unrestricted dropping]{
    \includegraphics[width=\columnwidth, clip=true, trim=0 0.1in 0 0]{figs/all_drop.pdf}
    \label{fig:policies.all_drop}
  }
  \vspace{-0.1in}
  \\
  \subfloat[source-only dropping]{
    \includegraphics[width=\columnwidth, clip=true, trim=0 0.1in 0 0]{figs/source_drop.pdf}
    \label{fig:policies.source_drop}
  }
  \vspace{-0.1in}
%   \\
%   \subfloat[sub-flow dropping]{
%     \includegraphics[width=\columnwidth]{figs/min_drop.pdf}
%     \label{fig:policies.min_drop}
%   }
  \end{center}
  \vspace{-0.1in}
  \caption{Comparison of dropping policies using metadata dependence graphs.
  Square nodes represent events where check are performed. Blue (dark) nodes
  indicate which nodes can be dropped.}
  \label{fig:policies.policies}
\end{figure}

In addition to deciding when dropping is required, trade-offs also exist in
deciding which events should be dropped.
The simplest policy is to drop any monitoring events when slack is less than or equal to zero.  However, this can result in
wasted work. For example, consider the metadata dependence graph shown in
Figure~\ref{fig:policies.all_drop}. Here, an edge from node {\tt A} to node
{\tt B} represents that if event {\tt A} is dropped, then due to its
invalidated metadata, it will cause event {\tt B} to be dropped. Square
nodes indicate events where monitoring checks are performed. In the
example, suppose that event {\tt E} is meant to perform a check operation but is dropped.
In this situation, the
monitoring operations that were done for events {\tt C} and {\tt D} were wasted
since their results were not used for any monitoring checks.
That is, by the time we decide to drop event {\tt E}, we have already 
updated metadata due to events {\tt C} and {\tt D} even though they are no longer needed.

### 2014-09-13 related.tex
Minor edits.

% Sampling
Statistical sampling is a method that has been applied to various debugging
techniques in order to reduce their performance overheads. For example, Liblit
et al. sampled program runs of thousands of users in order to find bugs
\cite{liblit-pldi05}. This idea has also been applied to detecting memory
leaks~\cite{chilimbi-asplos04}, dataflow analysis~\cite{greathouse-cgo11}, and dynamic information flow tracking\cite{testudo-micro08} and
other run-time monitoring techniques. 
These sampling-based techniques all limit the debugging capabilities in order
to provide lower performance overheads, which is one of the target applications of our architecture.
% Limited Monitoring
In terms of partial monitoring with adjustable overheads, the Quality Virtual Machine (QVM) is a
modification of the Java Virtual Machine (JVM) that supports run-time
monitoring with controllable overheads \cite{qvm-oopsla08}. Similarly, Huang et
al. created a framework for controlling the overheads of software-based
monitoring \cite{huang-sttt12}. 
Lo et al. \cite{lo-rtas14} developed a hardware architecture to limit
monitoring to meet deadlines for hard real-time systems.

>>>>

% Sampling
Statistical sampling is a method that has been applied to various debugging
techniques in order to reduce their performance overheads. For example, Liblit
et al. sampled program runs of thousands of users in order to find bugs
\cite{liblit-pldi05}. This idea has also been applied to detecting memory
leaks~\cite{chilimbi-asplos04}, dataflow analysis~\cite{greathouse-cgo11}, and
dynamic information flow tracking\cite{testudo-micro08}.
These sampling-based techniques all limit the debugging capabilities in order
to provide lower performance overheads, which is one of the target applications of our architecture.
% Limited Monitoring
In terms of partial monitoring with adjustable overheads, the Quality Virtual Machine (QVM) is a
modification of the Java Virtual Machine (JVM) that supports run-time
monitoring with controllable overheads \cite{qvm-oopsla08}. Similarly, Huang et
al. created a framework for controlling the overheads of software-based
monitoring \cite{huang-sttt12}. 
Lo et al. \cite{lo-rtas14} developed a hardware architecture to limit
monitoring to meet deadlines for hard real-time systems.
